% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2016 Jason R. Blevins <jrblevin@sdf.org>
% http://jblevins.org/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[11pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}

% Fonts
\usepackage[T1]{fontenc}


% Set your name here
\def\name{\textbf{Neven Caplar}}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {black hole-galaxy co-evolution, time-domain astronomy, AGN, CV},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.9in, 9.8in},
  left=0.7in,
  top=0.7in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\LARGE}
\subsectionfont{\rmfamily\bfseries\large}

\usepackage{paralist}
  \let\itemize\compactitem
  \let\enditemize\endcompactitem
  \let\enumerate\compactenum
  \let\endenumerate\endcompactenum
  \let\description\compactdesc
  \let\enddescription\endcompactdesc
  \pltopsep=\medskipamount
  \plitemsep=1pt
  \plparsep=1pt

% Other possible font commands include:
%\rmfamily is original
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.10em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.10em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.0em}
\setlist[enumerate]{parskip=0.0em}
\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.645\textwidth}
  Princeton University\\
  Astrophysical Department \\
  08540 - Princeton, NJ, USA	 \\
	4 Ivy Lane
\end{minipage}
\begin{minipage}[t]{0.345\textwidth}
  Phone: +1 609 787 8425 \\
  Web: \href{ www.ncaplar.com}{www.ncaplar.com} \\
  Email: \href{ncaplar@princeton.edu}{\nolinkurl{ncaplar@princeton.edu}} \\

\end{minipage}




\section*{Full publication list}


\subsection*{Peer-reviewed journals}

\begin{enumerate}



\item 2019, \textbf{N. Caplar}, T. Penna, S. Johnson, J. Greene \\
Nonstationarity of AGN variability: the only way to go is down!, submitted to ApJL\\

\item 2019, \textit{(corresponding author)} L. Sartori, K. Schawinski, B. Trakhtenbrot, \textbf{N. Caplar}, E. Treister, C. Zhang\\
A forward modelling approach to AGN variability – method
description and early applications, ApJ, 2019, 883, 139S\\


\item 2019, \textbf{N. Caplar}, S. Tacchella \\
Stochastic modeling of star-formation histories I: the scatter of the star-forming main sequence, 2019, MNRAS, 487, 3845C\\


\item 2018, L. Sartori, K. Schawinski, B. Trakhtenbrot, \textbf{N. Caplar}, E. Treister, M. Koss, M. Urry, C. Zhang \\
A model for AGN variability on multiple time-scales, 2018, MNRAS, 476L, 34S\\

\item 2018, \textbf{N. Caplar}, S. Lilly, B. Trakhtenbrot\\
AGN evolution from galaxy evolution viewpoint - II, ApJ, 2018, 867, 148C\\

\item 2017,  \textbf{N. Caplar}, S. J. Lilly, B. Trakhtenbrot   \\Optical variability of AGN in the PTF/iPTF survey, ApJ, 2017, 834, 111C   \\

\item 2017, A. Weigel, K. Schawinski,  \textbf{N. Caplar}, A. Carpineti, R. Hart, S. Kaviraj, W. Keel, S. Kruk, C. Lintott, R. Nichol, B. Simmons, R. Smethurst
\\    Galaxy Zoo:  Major galaxy mergers are not a significant quenching pathway, APJ, 2017, 845, 145W \\

\item 2017, A. Weigel, K. Schawinski,  \textbf{N. Caplar}, O. I. Wong, T. Ezequiel, B. Trakhtenbrot
\\    Two mass independent Eddington ratio distribution functions regulate black hole growth of blue and red 
galaxies in the local Universe, ApJ, 2017, 845, 134W \\


\item 2016, \textbf{N. Caplar}, S. Tacchella, S. Birrer \\ Quantitative evaluation of gender bias in astronomy,  2017, NatAs, 1E, 182C\\
 
\item 2015,  \textbf{N. Caplar}, S. J. Lilly, B. Trakhtenbrot  \\AGN evolution from a galaxy evolution viewpoint, ApJ,  2015, 811, 148C \\
  
 \item 2013,  \textbf{N. Caplar}, H. Stefancic  \\ Generalized models of unification of dark matter and dark energy, Phys. Rev. D, 2013, 87, 023510 \\


 
\end{enumerate}

\subsection*{Conference proceedings}
\begin{enumerate}
\item 2018, T. Naoyuki , T. Naruhisa,  A. Shimono, [and 111 others, including  \textbf{N. Caplar}] \\ Prime Focus Spectrograph (PFS) for the Subaru telescope: ongoing integration and future plans, Proceedings of the SPIE, Volume 10702, id. 107021C 12 pp. 

\item 2013,  \textbf{N. Caplar}, M. Suznjevic, M. Matijasevic  \\ Analysis of players' in-game performance vs rating: Case study of Heroes of Newerth, Foundation of Digital games 2013,  pp. 237-244  

\end{enumerate}

\newpage 


\end{document}
\section*{Internships and volunteering}
\begin{itemize}
  \item 2012, Jagellonian University
  \begin{itemize}
     
  
\item \textit{Supervisor:} Dr. Michael Ostrowski
 \item  \textit{Topic:} X-ray variability of knots in the jet of Centaurus A
\end{itemize}  
  \item 2010-2012, Institut Ruder Boskovic
  \begin{itemize}
\item \textit{Supervisor:} Dr. Hrvoje Stefancic
 \item  \textit{Topic:} Generalized models of unification of dark matter and dark energy
\end{itemize}  
\end{itemize}


\section*{References }

\begin{minipage}[t]{0.55\textwidth}
\begin{itemize}
\item \textbf{ dr. Simon J. Lilly, ETH Zurich}
\begin{itemize} \item simon.lilly@phys.ethz.ch
\item  Ph.D. thesis supervisor
\item 
\end{itemize}
\item \textbf{dr. Kevin Schawinski, ETH Zurich}
\begin{itemize} \item  kevin.schawinski@phys.ethz.ch
\item  
\item
\end{itemize}
\item  \textbf{dr. Dave Alexander, Durham University}
\begin{itemize} \item d.m.alexander@durham.ac.uk
\item  
\item 
\end{itemize}
\item \textbf{dr. Hrvoje Stefancic, Institut Ruder Boskovic}
\begin{itemize} \item  shrvoje@thphys.irb.hr
\item  Master thesis supervisor
\item  
\end{itemize}
\end{itemize}
\end{minipage}
\begin{minipage}[t]{0.45\textwidth}
\begin{itemize}
\item
\begin{itemize} 
\item Wolfgang-Pauli-Str. 27
\item 8093 Zurich-Switzerland
\item +41 44 633 38 28 
\end{itemize}
\vspace{0.7 cm}
\begin{itemize} 
\item Wolfgang-Pauli-Str. 27
\item 8093 Zurich-Switzerland
\item +41 44 633 07 51
\end{itemize}
\vspace{0.32 cm}
\begin{itemize} 
\item South Road, 335, Rochester Building
\item  DH1 Durham-United Kingdom
\item +44 191 3343594
\end{itemize}
\vspace{0.35 cm}
\begin{itemize} 
\item Bijenicka cesta 54
\item 10000 Zagreb-Croatia
\item +385 1 456 1032
\end{itemize}
\end{itemize}
\end{minipage}

% Footer
%\bigskip


\end{center}



