% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2016 Jason R. Blevins <jrblevin@sdf.org>
% http://jblevins.org/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[11pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}

% Fonts
\usepackage[T1]{fontenc}


% Set your name here
\def\name{\textbf{Neven Caplar}}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {black hole-galaxy co-evolution, time-domain astronomy, AGN, CV},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.9in, 9.5in},
  left=0.7in,
  top=0.7in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\LARGE}
\subsectionfont{\rmfamily\bfseries\large}

% Other possible font commands include:
%\rmfamily is original
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.15em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.495\textwidth}
  Department of Phyiscs \\
  Swiss Federal Institute of Technology \\
  8093-Zurich	 \\
  Wolfgang-Pauli Strasse 27 \\
  HIT J-33.3
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Phone: +41 44 63 33826 \\
  Web: \href{ http://people.phys.ethz.ch/~caplarn}{ http://people.phys.ethz.ch/$\sim$caplarn} \\
  Email: \href{caplarn@phys.ethz.ch}{\nolinkurl{caplarn@phys.ethz.ch}} \\
\end{minipage}



% \subsection*{Duke University, Department of Economics}
%
% \begin{itemize}
% \item Research Assistant, Jacob Vigdor, Summer 2005--Summer 2006.
% \item Teaching Assistant, Ph.D. Microeconomic Analysis, Thomas Nechyba, Fall 2005.
% \item Teaching Assistant, Ph.D. Game Theory, Curtis Taylor, Spring 2006.
% \item Instructor, Microeconomics Qualifier Camp, Summer 2006.
% \item Research Assistant, Han Hong, Fall 2006--Spring 2007.
% \item Research Assistant, Aprajit Mahajan and Alessandro Tarozzi,
%   October--November 2006, March--June 2007.
% \item Research Assistant, Shakeeb Khan and Christopher Timmins,
%   March--June 2007.
% \item Teaching Assistant, Ph.D. Econometrics II, Shakeeb Khan,
%   Spring 2007.
% \item Research Assistant, Peter Arcidiacono, Patrick Bayer,
%   and Paul Ellickson, Fall 2007--Spring 2009.
% \item Research Assistant, Shakeeb Khan, Fall 2009--Spring 2010.
% \item Research Assistant, Aprajit Mahajan, July--September 2009.
% \end{itemize}

% \subsection*{North Carolina State University, Department of Mathematics}
%
% \begin{itemize}
% \item Research Assistant, Moody Chu and Robert Funderlic,
%   Spring 2003--Fall 2004.
% \item Mathematics Tutor, Academic Support Program for Student Athletes,
%   Summer 2001.
% \end{itemize}

% \subsection*{Colorado School of Mines,
%   Department of Mathematical and Computer Sciences}
%
% \begin{itemize}
% \item Research Assistant, Willy Hereman, Summer 2002.
% \end{itemize}

\section*{Education}

\begin{itemize}
  \item 2013 - 2017 (expected), Ph.D., ETH Zurich
  \begin{itemize}
  \item \textit{Mentor:} dr. Simon J. Lilly, ETH Zurich
\item \textit{Title of the thesis:} Growth of variable active galactic nuclei

\end{itemize}  


%  \item 2012, intership, Jagellonian University
%  \begin{itemize}
%\item \textit{Mentor} dr. sc. Michael Ostrowski, Jagellonian University
%\end{itemize}


    % Received May 16, 2010
  \item 2005 - 2010, Masters degree, Faculty of Science, University of Zagreb
  \begin{itemize}
            \item \textit{Mentor:}
      dr. Hrvoje Stefancic, Institut Ruder Boskovic, Theoretical Physics division
    \item  \textit{Title of the thesis:}
  Unification models of dark energy and dark matter 

\end{itemize}  
\end{itemize}

\section*{Research}
\subsection*{Research interests}
 Main topics of my work include black hole-galaxy co-evolution, AGN physics and time domain astronomy. I have developed a phenomenological model which connects black hole evolution with the evolution of galaxies and make numbers of observational predictions, one being that the black hole to galaxy mass ratio must be evolving with redshift. %This projects involved analytical creation of the model, simulating the results and comparison with data.
 I have also measured and characterized the optical variability properties of AGNs in the Palomar Transient Factory Survey. I have found that AGN variability often exhibits more correlated behaviour then commonly used random-walk model. %This project involved development of calibration procedures and reduction of the big dataset.
 In future work I am interested in exploring the connection between the variability approach and the demographical approach to describe the ANG population. I am also interested in researching influence of the AGN spin on the variability and the growth of the accreting black holes.

\subsection*{Peer-Reviewed Journal Articles in Astronomy}

\begin{enumerate}
\item 2016, A. Weigel, K. Schawinski,  \textbf{N. Caplar}, O. I. Wong
\\    Two mass independent Eddington ratio distribution functions regulate black hole growth of blue and red 
galaxies in the local Universe, submitted to MNRAS \\

\item 2016,  \textbf{N. Caplar}, S. J. Lilly, B. Trakhtenbrot   \\Optical variability of AGN in the PTF/iPTF survey, submitted to APJ \\
 
\item 2015,  \textbf{N. Caplar}, S. J. Lilly, B. Trakhtenbrot  \\AGN evolution from a galaxy evolution viewpoint, 2015ApJ...811..148C \\
  
 \item 2013,  \textbf{N. Caplar}, H. Stefancic  \\ Generalized models of unification of dark matter and dark energy, Phys. Rev. D 87, 023510 (2013)   
\end{enumerate}
\newpage
% \subsection*{Scientific Software}
%
% \begin{itemize}
% \item \href{http://jblevins.org/research/pdest}{PDESolutionTester},
%   A Mathematica program for the symbolic verification of exact solutions
%   of nonlinear partial differential equations,
%   with Jeff Heath and Willy Hereman (2002).
% \item \href{http://jblevins.org/research/dfbr}{DFBR},
%   A Stata program for distribution-free estimation of heteroskedastic
%   binary response models,
%   with Shakeeb Khan (2009).
% \end{itemize}

\subsection*{Other Publications}

These publications include are works which are not directly connected to Astronomy. These are both big-data analysis papers for which I collected, manipulated and reduced the data.

\begin{enumerate}[resume]
\item 2016, \textbf{N. Caplar}, S. Tacchella, S. Birrer \\ Quantitative evaluation of gender bias in astronomy, to be submitted to Nature Astronomy 

\item 2013,  \textbf{N. Caplar}, M. Suznjevic, M. Matijasevic  \\ Analysis of players' in-game performance vs rating: Case study of Heroes of Newerth, Foundation of Digital games 2013,  pp. 237-244
\end{enumerate}

\subsection*{Proposals}
\begin{itemize}
\item 2013, F. Miniati, S. J. Lilly, \textbf{N. Caplar} \\ The connection between magnetised galactic outflows and high Faraday effect in the circumgalactic environment of intermediate redshift galaxies \\ Awarded 24 hours with VIMOS instrument
\item 2013, S. J. Lilly, F. Miniati,  \textbf{N. Caplar}, B. Gaensler, J. Farnes  \\ Testing the association of magnetized plasma with high redshift galaxies along the line of sight \\ 
Awarded 5 nights at NTT telescope
\end{itemize}


\section*{Seminar and Conference Presentations}

\begin{itemize}
\item 2016: Caltech (scheduled); Columbia (scheduled); University of Washington (scheduled); Stanford (scheduled); Shining from the heart of darkness: black hole accretion and jets, Katmandu, Nepal (conference, talk); AGN: what's in a name, Munich, Germany, (conference, talk)
\item 2015:
Black Hole Accretion and AGN Feedback, Shanghai, PRC, (conference, talk); Inaugural Zwicky Symposium, Braunwald, Switzerland, (conference, talk); Demographics and environment of AGN from multi-wavelength surveys Chania, Greece, (conference, talk); Unveiling the AGN/Galaxy Evolution, Puerto Varas, Chile, (conference, talk)
\item 2014:
COSMOS team meeting, Zagreb, Croatia, (conference, talk); Multiwavelength-surveys, Dubrovnik, Croatia, (conference, poster); Powerful AGN, Port Douglas, Australia, (conference, talk); The Formation and
Growth of Galaxies in the Young Universe, Obergurgl, Austria, (conference, talk)
\item 2012:
Karl-Franzens University, Graz, Austria, (invited talk); Jagellonian University, Krakow, Poland, (invited talk)
\item 2011:
European Summer Campus, Strasbourg, France, (conference/school, poster)
\end{itemize}


\section*{Teaching}
As a Ph.D. student at ETH Zurich I had the opportunity to contribute to the teaching
efforts at the Department of Physics. I committed most of that time helping with the introductory class in physics for chemist at ETH Zurich with $\sim$ 250 students. In the academic year 2015/2016 I lead the team which was in charge of preparing homework assignments and preparing the examination questions for this course.

\begin{itemize}
\item assistant: Advanced physics lab, Master course in physics, First year, ETH Zurich: Fall 2016
\item assistant: Physics for Chemists, Bachelor course in chemistry, Second year, ETH Zurich: Spring 2016, Fall 2015, Spring 2015, Fall 2014, Spring 2013, Fall 2013
\item assistant: Physical Cosmology, Master course in physics, First year, University of Zagreb: Spring 2011 
\end{itemize}

\section*{Miscellaneous}

\begin{itemize}
\item Programming Languages: Mathematica, Python, \LaTeX, CIAO, SQL

\item Since April 2015 I run astrodataiscool.com website, where I publish analysis of the data from astronomical and popular sources. The website gathered $\sim$20000 unique views. 
%\item \textit{Languages:}  \begin{itemize}
%\item Croatian: Native reading, writing, and speaking
%\item English: Fluent reading, writing, and speaking
%\item German : Basic reading, writing, and speaking
%\end{itemize}
\end{itemize}
\subsection*{Internships and volunteering}
\begin{itemize}
  \item 2012, Jagellonian University
  \begin{itemize}
     
  
\item \textit{Supervisor:} dr. Michael Ostrowski
 \item  \textit{Topic:} X-ray variability of knots in the jet of Centaurus A
\end{itemize}  
  \item 2010-2012, Institut Ruder Boskovic
  \begin{itemize}
\item \textit{Supervisor:} dr. Hrvoje Stefancic
 \item  \textit{Topic:} Generalized models of unification of dark matter and dark energy
\end{itemize}  
\end{itemize}



% Footer
%\bigskip

\begin{center}

{\small Last updated: \today}

\end{center}



\end{document}